Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance

### 2022-10-04 text/Manuscript.Rmd
figure 4 legend

---
title: Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance
  in zooplankton
author: "Kei Jokura, Nobuo Ueda, Martin Gühmann, Luis Alfonso Yañez-Guerra, Gáspár Jékely"
date: '*Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4
  4QD, UK*'
output:
  pdf_document:
    latex_engine: lualatex
    template: default
  html_document:
    theme: lumen
  word_document: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

![**Figure 4. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** (A) The intensity of DAF-FM in INNOS changes over time when cPRC (top) and other cells (NC) (bottom) are stimulated with UV (405 nm). Hereafter, light purple squares indicate the timing of UV stimulation, gray traces show the optical responses to individual intensities, each intensities are normalized (ΔF/F0) and the dark lines and the bands show the mean value and the standard error range of the mean. (B) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in WT (purple) and NOS mutant (NOSΔ23) (gray) larvae. (C) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 knockdown by morpholino (NITGC1-MO1 and 2) larvae. (D) Co-expression analysis image of the cPRC marker gene (NIT-GC1: magenta) and the INNOS marker gene (RYa-pNP: green) using in situ HCR. White arrowheads indicate INNOS strongly expressing RYa-pNP. (E) INNOS (blue dashed line) identified from calcium imaging using GCaMP6s by their position in relation to the cPRC (purple dashed line). (F) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INNOS (blue) when cPRC is stimulated with UV in WT (left) and NOS mutant (NOSΔ11: right) larvae. (G) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INRGW (green) when the cPRC are stimulated with UV in WT (left) and NOS mutant (NOSΔ23: right) larvae. (H)(I)(J)](../figures/Fig4.png){width="100%"}

>>>>

---
title: Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance
  in zooplankton
author: "Kei Jokura, Nobuo Ueda, Martin Gühmann, Luis Alfonso Yañez-Guerra, Kyle C. A. Wedgwood, Piotr Słowiński, Gáspár Jékely"
date: "*Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4
  4QD, UK*"
output:
  pdf_document:
    latex_engine: lualatex
    template: default
  html_document:
    theme: lumen
  word_document: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

![**Figure 4. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** (A) The intensity of DAF-FM in INNOS changes over time when cPRC (green) and other cells (NC) (gray) are stimulated with UV/violet (405 nm). Hereafter, light purple squares indicate the timing of 405 nm light stimulation, the transparent lines show the optical responses to individual intensities, each intensities are normalized (ΔF/F0) and the dark trace lines and the shaded bands show the mean value and the standard error range of the mean. (B and C) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in WT (dark yellow) and NOS mutant (B: NOSΔ11/Δ11, B: NOSΔ23/Δ23) (light yellow) larvae. (D and G) Correlation (Pearson’s r) map of neuronal activity of the cPRC, IN-NOS, IN-RGWa and Ser-h1 neurons. Correlation values were calculated relative to the cPRC (D) or IN-NOS (G). (E) Changes over time in GCaMP6s intensities in IN-NOS when cPRC is stimulated with UV in WT (dark purple) and NOS mutant (light purple) larvae. (F) Changes over time in GCaMP6s intensities in IN-NOS when cPRC is stimulated with UV in NIT-GC2 morphants larvae. (H) Changes over time in GCaMP6s intensities in IN-RGWa when cPRC is stimulated with UV in WT (dark blue) and NOS mutant (light blue) larvae. (I) Changes over time in GCaMP6s intensities in Ser-h1 when cPRC is stimulated with UV in WT (dark red) and NOS mutant (light red) larvae.](../figures/Fig4.png){width="100%"}
